\plaintitle

### 2017-01-04 drafts/labor/introduction.tex
some changes to piecework lit's beginning thinking more carefully about how i want to frame and organize the whole section. in slack i told msb that i'd probably merge the definition and primer stuff together; they don't really make sense apart anyway, and both feel a little too thin

\topic{The past decade has seen a flourishing of \textit{on--demand work},
largely driven by the reformulation of work as
constituent parts of larger tasks.}
This framing of work into modular
has enabled the computational hiring \& management of workers at scale~\cite{howe2008crowdsourcing,Bigham2014,crowdworkFuture}.
Distributed paid participants then engage in work whenever their schedules allow,
with little to no awareness of the broader context of the work, and
often with fleeting identities and associations~\cite{martin2014being,uberAlgorithm}.
In this paper, we use the term on--demand work to join a pair of related phenomena:
first, \textit{crowd work}, on platforms such as Amazon Mechanical Turk (AMT) and other sites of (predominantly) information work;
and second, \textit{gig work}, often as platforms for one--off jobs, like driving, courier services, or administrative support.
The realization that complex goals can be accomplished by directing and managing crowds of workers spurred industry to flock to sites of labor
such as AMT to explore the limits of this distributed, on--demand workforce.
Researchers have also taken to the space in earnest,
developing systems and designs that enable new forms of production
(e.g. \cite{bernsteinSoylent,vizwiz,paolacci2010running}).

@@

\topic{This body of research has broadly sought to answer one central question:
What does the future hold for on--demand work and those who do it?}
Researchers have offered insights on this question along three major threads:
% \begin{numberlist}[itemjoin*={.~And~},itemjoin={.~}]
  First, \nameref{sec:complexity}?
        Specifically,
        \begin{inlinelist}[label=(\alph*)]
          \item How complex are the goals that crowd work can accomplish?, and
          \item What kinds of goals and industries may eventually utilize it?
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364}.
  Second, \nameref{sec:decomposition}
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}.
  And third, \nameref{sec:relationships}?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}.
% \end{numberlist}

@@

More concretely, by looking at on--demand work as
an instantiation (or even a continuation) of piecework,
and by interrogating patterns that the corresponding literature predicts
on this basis, we can
% \begin{numberlist}[itemjoin*={; and },itemjoin={;~}]
first, make sense of past events as part of a much larger series of an interrelated phenomenon;
second, reflect on differences in the factors that impacted piecework historically and their impact on--demand work today;
and third, to some extent, offer predictions of what on--demand work researchers,
and workers themselves,
might expect to see on the horizon.
% \end{numberlist}
For example, we will draw on the piecework literature regarding task decomposition,
which was historically limited by shortcomings in measurement and instrumentation, and
leverage that understanding to suggest how modern technology affects this mechanism in on--demand work
--- namely, by enabling precise tracking and measurement of workers via algorithms and software.

We organize this paper as follows:
% \begin{numberlist}[itemjoin*={; and },itemjoin={;~}]
first, we review the definition and historical arc of piecework
to lay groundwork and make clear the analogy to on--demand work
(which we'll call \textit{crowd work} hereon
for consistency with the existing literature);
second, we interrogate the three major research questions above using the lens of piecework. 
We will identify similarities and differences between piecework as historically understood and
on--demand work as we know it today;
third, we will make predictions of future developments based on how those similarities and differences influenced piecework;
finally, we will offer implications for researchers and practitioners based on our results.
% \end{numberlist}

>>>>

\topic{The past decade has seen a flourishing of \textit{on--demand work},
largely driven by the reformulation of work as
constituent parts of larger tasks.}
This framing of work into modular
has enabled the computational hiring \& management of workers at scale~\cite{howe2008crowdsourcing,Bigham2014,crowdworkFuture}.
Distributed paid participants then engage in work whenever their schedules allow,
with little to no awareness of the broader context of the work, and
often with fleeting identities and associations~\cite{martin2014being,uberAlgorithm}.
In this paper, we use ``on--demand work'' to capture a pair of related phenomena:
first, \textit{crowd work}, on platforms such as Amazon Mechanical Turk (AMT) and other sites of (predominantly) information work;
and second, \textit{gig work}, often as platforms for one--off jobs, like driving, courier services, or administrative support.
The realization that complex goals can be accomplished by directing and managing crowds of workers spurred industry to flock to sites of labor
such as AMT to explore the limits of this distributed, on--demand workforce.
Researchers have also taken to the space in earnest,
developing systems and designs that enable new forms of production
(e.g. \cite{bernsteinSoylent,vizwiz,paolacci2010running}).

@@

\topic{This body of research has broadly sought to answer one central question:
What does the future hold for on--demand work and those who do it?}
Researchers have offered insights on this question along three major threads:
First, \nameref{sec:complexity}?
      Specifically,
      \begin{inlinelist}[label=(\alph*)]
        \item How complex are the goals that crowd work can accomplish?, and
        \item What kinds of goals and industries may eventually utilize it?
      \end{inlinelist}
      \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
            Nebeling:2016:WCW:2858036.2858169,
            Hahn:2016:KAB:2858036.2858364}.
Second, \nameref{sec:decomposition}
      \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
            LykourentzouPersonalityMatters,KucherbaevReLauncher,
            Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
            Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}.
And third, \nameref{sec:relationships}?
      \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
            whyWouldAnyoneBrewer,takingAHITMcInnis}.
% \end{numberlist}

@@

More concretely, by looking at on--demand work as
an instantiation (or even a continuation) of piecework,
and by interrogating patterns that the corresponding literature predicts
on this basis, we can
first, make sense of past events as part of a much larger series of an interrelated phenomenon;
second, reflect on differences in the factors that impacted piecework historically and their impact on--demand work today;
and third, to some extent, offer predictions of what on--demand work researchers,
and workers themselves,
might expect to see on the horizon.
% \end{numberlist}
For example, we will draw on the piecework literature regarding task decomposition,
which was historically limited by shortcomings in measurement and instrumentation, and
leverage that understanding to suggest how modern technology affects this mechanism in on--demand work
--- namely, by enabling precise tracking and measurement of workers via algorithms and software.

We organize this paper as follows:
first, we review the definition and historical arc of piecework
to lay groundwork and make clear the analogy to on--demand work
(which we'll call \textit{crowd work} hereon
for consistency with the existing literature);
second, we interrogate the three major research questions above using the lens of piecework. 
We will identify similarities and differences between piecework as historically understood and
on--demand work as we know it today;
third, we will make predictions of future developments based on how those similarities and differences influenced piecework;
finally, we will offer implications for researchers and practitioners based on our results.
% \end{numberlist}
